Concurrent Programming with CXL

### 2020-06-17 book/paper.tex
Working on exercises

Figure~\ref{fig:triangle} gives a simple example of a CXL program.
(The code for examples in this book can be found in the \texttt{code} folder under
the name listed in the caption of the example.)
It is sequential and has a method \texttt{square} that takes
an integer number as argument.  Each method has a variable called
\texttt{result} that eventually contains the result of the
method (there is no \texttt{return} statement in CXL).  The method
also has a variable called \texttt{n} containing the value of the
argument.  The \texttt{x..y} notation generates a set containing the numbers
from~\texttt{x} to~\texttt{y} (inclusive).  The last two lines in the program are
the most interesting.
The first assigns to \texttt{x} some unspecified value in the range \texttt{0..N}
and the second verifies that $\mathtt{triangle}(x)$ equals $x(x+1)/2$.

@@

\section*{Exercises}
\begin{enumerate}
\item See what happens if, instead of initializing \texttt{result} to 0,
you initialize it to 1.  (You do not need to understand the error report at this time.)
\item Write a program that computes factorials.
\end{enumerate}

@@

>>>>

Figure~\ref{fig:triangle} shows a simple example of a CXL program.
(The code for examples in this book can be found in the \texttt{code} folder under
the name listed in the caption of the example.)
It is sequential and has a method \texttt{square} that takes
an integer number as argument.  Each method has a variable called
\texttt{result} that eventually contains the result of the
method (there is no \texttt{return} statement in CXL).  The method
also has a variable called \texttt{n} containing the value of the
argument.  The \texttt{x..y} notation generates a set containing the numbers
from~\texttt{x} to~\texttt{y} (inclusive).  The last two lines in the program are
the most interesting.
The first assigns to \texttt{x} some unspecified value in the range \texttt{0..N}
and the second verifies that $\mathtt{triangle}(x)$ equals $x(x+1)/2$.

@@

\section*{Exercises}
\begin{enumerate}
\item See what happens if, instead of initializing \texttt{result} to 0,
you initialize it to 1.  (You do not need to understand the error report at this time.)
\item Write a CXL program that computes squares by repeated adding.  So the program
should compute the square of $x$ by adding $x$ to an initial value of 0 $x$ times.
\end{enumerate}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/UpEnter.cxl}
\end{code}
\caption{[UpEnter.py] Broken attempt at fixing the code of Figure~\ref{fig:inc}.}
\label{fig:incenter}
\end{figure}
